\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\usepackage[capitalize, nameinlink]{cleveref}   % Specify reference types (e.g. Table, Figure)
\usepackage{setspace}
\usepackage{svg}

\include{settings}

\begin{document}

\input{title_page}
\clearpage

\doublespacing
\tableofcontents
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abstract}

Architecture projects often involve both large structures and detailed components, and are often highly geometric. Digital architecture designs (i.e., created through the use of CAD) are often stored in a vector (shape-based) format for convenient editing. Raster (pixel-based) images, such as photographs, are not as easily used for these purposes, which largely diminishes their usability for the design process. Our project aims to develop a image vectorization method (i.e., a tool to convert from raster to vector format) specialized towards architecture images and explores the potential of vector-based images in the architecture design process and in machine learning preprocessing.

There are several general methods for image vectorization -- we propose a sampling-based vectorization method involving three steps. The image is sampled using a blue-noise sampling technique, which extracts the high frequency components in the image and filters out the less important pixels. The sampled point cloud is then simplified to reduce the number of vectors in the final drawing. Finally, the last step involves converting the point cloud to an efficient vector representation. This vector representation is saved as some vector image format, such as SVG.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goal}

Our project aims to provide an end-to-end image vectorization tool. Vectorization is the process of generating a vector image that is faithful to the input raster image. We aim to specialize in architectural images specifically, which should allow us to optimize our project for this use case. Architectural images are usually highly geometric, which should allow for an efficient vector representation. In theory, a highly geometric image should have a vector representation that is more efficient than the original image. Of course, with real images, the image will not be perfectly geometric. However, we are comfortable with information loss, as long as the main content of the image is preserved; we will develop a suitable loss metric to quantify the representation efficiency and error loss.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Previous Works and Motivation}

Some of the first image vectorization tools implemented edge tracing, which works well for simple shapes, and especially in black-and-white (or similarly color-thresholded) images. However, architectural images are more complex and can have wide range of colors, rendering traditional methods ineffective. A new vectorization method is needed to work effectively for colored complex images and to generate vector representations that are easy to use for architects. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% insert motivation for specializing in architecture

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Methods}

Multiple methods have been considered for this project, including traditional edge tracing, machine learning, and sampling. These methods are compared, and we determined that the sampling method is the most effective for our use case.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Potential Applications}

Our project can potentially be applied to the architecture design process, along with vector-based machine learning. One of the use cases we envision is to take a photo of an architectural design, use our project to process that image, and use the vector-based output to easily edit the image. Another potential use case is for vector-based machine learning. In computer vision, image data used as input is traditionally in raster format -- there is little research performed on how well deep learning performs on vector-based image inputs. We imagine that due to the efficiency of its representation, especially for highly-geometric shapes, we may be able to have more useful information in the deep learning model from the outset. In other words, a conversion to vector-based models, in which the shapes contain meaningful information about the image, may be useful as a machine learning preprocessing step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Background}
\input{sections/background}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Related Work}
\input{sections/related_work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Methods}
\input{sections/methods}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Conclusion}

Image vectorization is the process of converting a raster image to a vector image, and may lead to efficiency gains for highly vectorized images. While vectorization has been used successfully on simple vector-based input images in the past such as map or typography images, we aim to improve its output on highly-geometric but less-exact images, such as architectural images. We believe that this may be useful in the architectural design process, and perhaps in other design processes whose subject is highly geometric.

We have implemented a basic framework for vectorizing raster images, primarily based on \cite{zhao2013image}. We can take an input image, perform sampling on the image, triangulate the sampled points, and produce an output image. So far we have yet to optimize this method towards architecture -- this will involve optimization stages after producing the mesh.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Future Work}

In the upcoming semester, we would like to experiment with different vectorization approaches. This may involve different sampling methods or different optimizations. We may choose a different method for generating vectors from the sampled points. Currently, we are using a standard Delaunay triangulation, although there may be alternative methods available.

We may change our evaluation metric if we discover a better metric. We will rank each of our approaches according to our evaluation metric. By the end of the upcoming semester, we will also produce a presentation describing our results, along with a final report that contains the final decisions made for our project.

An approximate timeline for the spring semester may look like:
\begin{description}
\item[January] Begin work on mesh optimization, review prior work.
\item[February] Continue mesh optimization, clearly define evaluation metrics.
\item[March] Begin gathering results and evaluating using given metric.
\item[April] Finish result-gathering, begin final report and presentation.
\item[May] Complete final report and presentation, present results.
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\printbibliography[
    heading=bibnumbered,
    title={References}
]

\end{document}
